Brownian Dynein Model

### 2015-11-02 latex/derivation.tex
Modifying derivation.tex

@@

\subsection{$X_t$ and $Y_t$}

>>>>

\begin{align}
  \dot{X}_{nm} &= \frac{1}{{2L_n^{-3}LL_s}}\left(-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2\right)\dot{L}_n\\ &+ \frac{2L_nL^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_n^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_s^2L_{f}\dot{L}_f - 2L_nL_{f}^2\dot{L}_n - 2L_n^2L_{f}\dot{L}_f + 2L_t^2L_{f}\dot{L}_f}{4L_n^2LL_s}\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2\dot{L}_n - 2L_fL^2\dot{L}_f + 2L^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L^2L_{f}\dot{L}_f  + 4L_{f}^3\dot{L}_f}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\frac{d}{dt} \left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
    - \frac{2L_nL_{s}^2\dot{L}_n + 2L_s^2L_{n}\dot{L}_n + 4L_{n}^3\dot{L}_n - 2L_t^2L_{n}\dot{L}_n - 2L_nL_{t}^2\dot{L}_n}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\\
\end{align}

@@

\subsection{Solving for $X_{fm}$ and $Y_{fm}$}
The near motor and far motor cases are equivalent. If the farbound binding angles are set to take the same values and positions as $\theta_1$ and $\theta_2$, then we can see that

\subsection{Solving for $X_t$ and $Y_t$}
